Condition-based Maintenance and Production Policies for Multi-Unit Systems

### 2018-06-22 report/paper_scm.tex
Final changes to model

 We define the set of possible production rates for unit $i$ in state $x_i$ $U(x_i)$ as follows
$$
U(x_i) = \begin{cases}
\{0, 1/m, \dots, 1\} & \text{ if } x_i \neq L, \\
\{0\} & \text{ if } x_i = L.
\end{cases}
$$
Let $u = (u_1, \dots, u_n)$ denote the production rate of all units in the system. The total production rate of the system is restricted to $\pi$, i.e., $ \sum_{i=1}^{n}u_i = \pi$. This results in the following action space for the system in state $x$
$$
U(x) = \left\{ u  :  \sum_{i=1}^{n}u_i = \pi, u_i \in U(x_i) \enskip \forall i \in \mathcal{I} \right\}.
$$
Note that the production action space decreases from $(m+1)^n$ elements to ${n + \pi - 1} \choose{\pi - 1} $ by restriction the total production rate to the value $\pi$.

@@

\section{Numerical results two-unit system}
In this section I will discuss the key features of the optimal maintenance and production policy for a two-unit system using the MDP as described in Section 3. Similar to \cite{OLDEKEIZER2018319} we select preventive maintenance costs $c_\text{pm} = 5$, set-up cost $C = 4$, and a corrective maintenance cost $c_\text{cm} = 11$. The rate parameter under the maximum production rate is $\lambda_{\text{max}} = 0.7$ and the scale parameter $\gamma = 1$. The failure level $L$ and the number of possible production rates are set to 25 and 26, respectively. We vary the total production $\pi$ with values 20, 30, 40 and 48. For $\pi = 20$, one unit can handle all the production, whereas for $\pi = 48$ we do not have much overcapacity in the system. We set $\alpha = 0.1$, such that the deterioration rate is low when the unit is not producing. We consider three different values for $\beta$:  $0$ (deterioration rate does not depend on production), $1$ (deterioration rate depends linearly on production) and $1.5$ (deterioration rate is convex in the production).

>>>>

 We define the set of possible production rates for unit $i$ in state $x_i$ $U(x_i)$ as follows
$$
U(x_i) = \begin{cases}
\{0, 1/m, \dots, 1\} & \text{ if } x_i \neq L, \\
\{0\} & \text{ if } x_i = L.
\end{cases}
$$
Let $u = (u_1, \dots, u_n)$ denote the production rate of all units in the system. The total production rate of the system is restricted to $\pi$, i.e., $ \sum_{i=1}^{n}u_i = \pi$. This results in the following action space for the system in state $x$
$$
U(x) = \left\{ u  :  \sum_{i=1}^{n}u_i = \pi, u_i \in U(x_i) \enskip \forall i \in \mathcal{I} \right\}.
$$

Note that the production action space decreases from $(m+1)^n$ elements to ${n + \pi - 1} \choose{\pi - 1} $ by restriction the total production rate to the value $\pi$. Observe that a $1$-out-of-$N$ can be obtained if we set $\pi$ to 1, and, more generally, a $k$-out-of-$N$ system if we set $\pi$ equal to $k$.

@@

\section{Numerical results two-unit system}
In this section I will discuss the key features of the optimal maintenance and production policy for a two-unit system using the MDP as described in Section 3. I normalise the corrective maintenance cost to $c_\text{cm}$ to 1, the fixed cost is set to $C = 0.4$ and preventative maintenance $c_\text{pm}$ to 0.2, i.e., the cost of performing corrective maintenance is five times higher than preventive maintenance. For the deterioration process we set the mean and variance equal to 1. The rate and scale parameter of the gamma process are implicitly defined for any choice of the mean and variance parameter. The number of deterioration states and production actions for each unit is set to 26, i.e., $L = 25$ and $m = 25$. The base total production value $\pi$ is set to 1 (which results in a $1$-out-of-$N$ system). The parameters for the function $g$ are set to $\alpha = 0.1$, such that the deterioration rate is low when the unit is not producing, and $\beta = 1.5$.
